### 2017-05-11 conclusion.tex
Add files via upload

Chapter \ref{paper2} includes an analysis of two long term, time-continuous climatologies of hemispherical sUHI, one in Basel, Switzerland and another in Vancouver, Canada. sUHI for both study sites shows significant diurnal, day-to-day, and seasonal variability. sUHI is highly dependent on meteorological conditions, particularly accumulated solar radiation over a day and wind velocity. However, as sUHI is the result of differences in heating and cooling rates between the city and its non urban surroundings, its relationship to meteorological controls is complex. Analysis of sUHI development under a range of mid-latitude synoptic conditions lead to the development of the first observationally-supported, generalizable model for sUHI development presented in Section \ref{gen}.

@@

The complex nature of the urban surface introduces myriad shortcomings and biases into conventional remote sensing of urban thermal climates - this method is no exception. Sensor placement sensitivity tests in Section \ref{placement} corroborate findings in \citet{Roberts2010,Adderley2015} and indicate that longwave radiation upwelling from the urban surface as measured from a downward-facing radiometer is spatially variant when measured from heights below approximately three to five times mean building height. Most pyrgeometers (including those used in this study) are mounted below this height and are subject to a bias towards facets that make up a disproportionately large fraction of the sensor FOV. For sensors mounted at less than optimal heights, the effect of this bias on derived T\textsubscript{hem, r} is largely dependent on sensor placement relative to rooftop facets, with better performance when mounted offset from roof areas. Pyrgeometers at the Sperrstrasse and Sunset tower sites are placed far enough from rooftops to render this bias relatively small. However, future studies should strive for pyrgeometer heights that are more optimal not only to yield more geometrically representative T\textsubscript{hem, r}, but also to ensure irradiances are representative of the complete urban longwave emission in energy balance assessments.

@@

While satellite assessment of sUHI and urban T\textsubscript{surf} has been essential in elucidating the spatial character of urban effects on T\textsubscript{surf}, several of the questions posed nearly 30 years ago in \citet{Roth1989} remain unanswered. This should prompt not only critical assessment of the urban T\textsubscript{surf} record, but also the development and use of novel methods to fill knowledge gaps, quantify biases, and uncover methodological shortcomings. This method, and in particular its parameterization, is intended to aid in such an endeavor as it is readily adapted to other study sites and requires few meteorological inputs. According to the Urban Flux Network (\href{http://fluxnet.fluxdata.org/}{Urbanflux}) currently there are 26 operational flux towers in urban areas instrumented for assessment of the net radiation budget. In addition, many other datasets of urban energy balances from inactive and decommissioned towers and from campaigns not indexed by Urbanflux are available for analysis via this method. These datasets span several continents and climatic zones, and characterize energy balances for cities over a range of developing and developed nations, with many operational over very long (5+ years) time scales. Thus, the application of this method over existing untapped datasets, and as a component of future energy balance assessments, can not only could provide a wealth of novel urban T\textsubscript{surf} and sUHI analyses for urban climatology and could also can provide for analysis outside the traditional purview of urban climatology. The character of the urban effect on land T\textsubscript{surf} (and climate at large) has complex, multifaceted relationships with the layout, size, population density, and development regimes of a given city as well as factors that are more difficult to observe, including social structure and culture. Long term, time continuous analysis of urban T\textsubscript{surf} and sUHI can help to better understand these links.

>>>>

Chapter \ref{paper2} includes an analysis of two long term, time-continuous climatologies of hemispherical sUHI, one in Basel, Switzerland and another in Vancouver, Canada. sUHI for both study sites shows significant diurnal, day-to-day, and seasonal variability. sUHI is highly dependent on meteorological conditions, particularly accumulated solar radiation over a day and wind velocity. However, as sUHI is the result of differences in heating and cooling rates between the city and its non urban surroundings, its relationship to meteorological controls is complex. Analysis of sUHI development under a range of mid-latitude synoptic conditions lead to the development of the first observationally-supported, generalizable model for sUHI development presented in Section \ref{gen_mod}.

@@

The complex nature of the urban surface introduces myriad shortcomings and biases into conventional remote sensing of urban thermal climates - this method is no exception. Sensor placement sensitivity tests in Section \ref{placement} corroborate findings in \citet{Roberts2010} and \citet{Adderley2015}. They indicate that longwave radiation upwelling from the urban surface as measured from a downward-facing radiometer is spatially variant when measured from heights below approximately three to five times mean building height. Most pyrgeometers (including those used in this study) are mounted below this height and are subject to a bias towards facets that make up a disproportionately large fraction of the sensor FOV. For sensors mounted at less than optimal heights, the effect of this bias on derived T\textsubscript{hem, r} is largely dependent on sensor placement relative to rooftop facets, with better performance when mounted offset from roof areas. Pyrgeometers at the Sperrstrasse and Sunset tower sites are placed far enough from rooftops to render this bias relatively small. However, future studies should strive for pyrgeometer heights that are more optimal not only to yield more geometrically representative T\textsubscript{hem, r}, but also to ensure irradiances are representative of the complete urban longwave emission in energy balance assessments.

@@

While satellite assessment of sUHI and urban T\textsubscript{surf} has been essential in elucidating the spatial character of urban effects on T\textsubscript{surf}, several of the questions posed nearly 30 years ago in \citet{Roth1989} remain unanswered. This should prompt not only critical assessment of the urban T\textsubscript{surf} record, but also the development and use of novel methods to fill knowledge gaps, quantify biases, and uncover methodological shortcomings. This method, and in particular its parameterization, is intended to aid in such an endeavor as it is readily adapted to other study sites and requires few meteorological inputs. According to the Urban Flux Network (\href{http://fluxnet.fluxdata.org/}{Urbanflux}) currently there are 26 operational flux towers in urban areas instrumented for assessment of the net radiation budget. In addition, many other datasets of urban energy balances from inactive and decommissioned towers and from campaigns not indexed by Urbanflux are available for analysis via this method. These datasets span several continents and climatic zones, and characterize energy balances for cities over a range of developing and developed nations, with many operational over very long (5+ year) time scales. Thus, the application of this method over existing untapped datasets, and as a component of future energy balance assessments, can not only could provide a wealth of novel urban T\textsubscript{surf} and sUHI analyses for urban climatology and could also can provide for analysis outside the traditional purview of urban climatology. The character of the urban effect on land T\textsubscript{surf} (and climate at large) has complex, multifaceted relationships with the layout, size, population density, and development regimes of a given city as well as factors that are more difficult to observe, including social structure and culture. Long term, time continuous analysis of urban T\textsubscript{surf} and sUHI can help to better understand these links.

### 2017-05-11 introduction.tex
Add files via upload

The temperature of a surface (urban or otherwise) at its interface with the atmosphere is defined as the net result of the surface energy balance \citep{Oke2017}, wherein change in temperature at time $t$ for a surface with thickness $z$ and heat capacity $C$ can be solved as,

\begin{equation}
	C~\frac{\partial \text{T\textsubscript{surf}}}{\partial t}~z = Q^*+ Q_F - Q_H - Q_E - \Delta Q_A - \Delta Q_G
\end{equation}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,
	height=7in,
	keepaspectratio]{model}
	\caption{Projected FOVs for a narrow-FOV sensor at nadir and oblique angles, and a wide-FOV hemispherical sensor viewing an idealized urban array with building width \textit{H}, height 2\textit{H}, and inter element spacing \textit{H}. Figure from Adderley et al. (2015).}
	\label{model}
\end{figure}

>>>>

The temperature of a surface (urban or otherwise) at its interface with the atmosphere is defined as the net result of the surface energy balance \citep{Oke2017}, wherein change in temperature at time $t$ for a surface with thickness $z_t$ and heat capacity $C$ can be solved as,

\begin{equation}
	C~\frac{\partial \text{T\textsubscript{surf}}}{\partial t}~z_t = Q^*+ Q_F - Q_H - Q_E - \Delta Q_A - \Delta Q_G
\end{equation}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=15cm,
	height=7in,
	keepaspectratio]{model}
	\caption{Projected FOVs for a narrow-FOV sensor at nadir and oblique angles, and a wide-FOV hemispherical sensor viewing an idealized urban array with building width \textit{W}, height 2\textit{W}, and inter element spacing \textit{W}. Figure from Adderley et al. (2015).}
	\label{model}
\end{figure}
